Notation

### 2018-04-11 notation.Rmd
Added stuff to notation, and added data.

>>>>

# Notation Dictionary

\begin{tabular}{l p{5cm}}
$\theta_i$ & Effect parameter of study $i$, also called the study results.\\[1.1ex]
$T_i$ & Estimate of study $i$\\[1.1ex]
$v_i$ & Variance of estimate for study $i$\\[1.1ex]
$p_i$ & $p$-value for study $i$\\[1.1ex]
$1 - \beta_i$ & Power for study $i$\\[1.1ex]
$\theta_{ij}$ & Effect parameter of study $i$ for finding $j$\\[1.1ex]
$T_{ij}$ & Estimate of study $i$ for finding $j$\\[1.1ex]
$v_{ij}$ & Variance of estimate for study $i$ for finding $j$\\[1.1ex]
$p_{ij}$ & $p$-value for study $i$ for finding $j$\\[1.1ex]
$1 - \beta_{ij}$ & Power for study $i$ for finding $j$\\[1.1ex]
\end{tabular}
